A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-21 4_method.tex
fix bisector angle and describe discretization of parabolas

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \sin(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This ratio can be immediately applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex and another vertex or line segment, we could exactly determine at which location $\frac{\partial R}{\partial x} > \sin(\alpha_\text{max} / 2)$.
However, because we have discretized such segments, we can approximate the location by applying our ratio based significance measure on the piecewise linear approximating segments directly.

@@

\subsubsection{Transitioning to insignificance}
In significant regions of the VQ we employ the approach of applying the optimal bead counts and employing transitioning, while in insignificant regions the beading is only governed by the beading of locations with locally optimal feature radius.
Significant bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$.
At the end of such chain $v$ we may need to transition from the former approach to the latter.
This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \sin(\alpha_\text{max} / 2)$ then the bead count assigned by the significant region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
See \cref{transition_to_insignificance_problem}.

>>>>

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existance of significant regions.

@@

\subsubsection{Transitioning to insignificance}
In significant regions of the VQ we employ the approach of applying the optimal bead counts and employing transitioning, while in insignificant regions the beading is only governed by the beading of locations with locally optimal feature radius.
Significant bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$.
At the end of such chain $v$ we may need to transition from the former approach to the latter.
This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the significant region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
See \cref{transition_to_insignificance_problem}.
